Compiling refinement types to dependent types

### 2020-07-25 tex/paper.tex
Use bold font for \unit and \unitc
It's a constant after all, not a variable.
Update T-Unit description
\Tranctx doesn't map into well-formedness proofs of the context in the
core language.

\newcommand{\unit}{u}
\newcommand{\Unit}{\textbf{Unit}}
\newcommand{\unitc}{\hat{u}}
\newcommand{\Unitc}{\widehat{\textbf{Unit}}}
\newcommand{\Int}{\textbf{Int}}
\newcommand{\ctxok}{\text{~ok}}
\newcommand{\fresh}{\text{~fresh name}}

@@

\begin{itemize}
  \item \textsc{T-Unit}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok}
                  {\nonterm G \vdash \unit : \{ \gterm v : \Unit | \top \}}
          \longmapsto
        \inferrule{~}
                  {\nonterm{GC} \vdash \unitc : \Unitc}, \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok).
    \end{align*}
    This rule has a single premise $\nonterm G \ctxok$ that the surface context is well-formed.
    We use $\Tranctx$ to translate the surface derivation of that premise into the core one,
    and extract the resulting context $\nonterm{GC}$.
    We then use that context for \textsc{CT-UnitTerm}.

>>>>

\newcommand{\unit}{\textbf{u}}
\newcommand{\Unit}{\textbf{Unit}}
\newcommand{\unitc}{\hat{\textbf{u}}}
\newcommand{\Unitc}{\widehat{\textbf{Unit}}}
\newcommand{\Int}{\textbf{Int}}
\newcommand{\ctxok}{\text{~ok}}
\newcommand{\fresh}{\text{~fresh name}}

@@

\begin{itemize}
  \item \textsc{T-Unit}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok}
                  {\nonterm G \vdash \unit : \{ \gterm v : \Unit | \top \}}
          \longmapsto
        \inferrule{~}
                  {\nonterm{GC} \vdash \unitc : \Unitc}, \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok).
    \end{align*}
    This rule has a single premise $\nonterm G \ctxok$ that the surface context is well-formed.
    $\Tranctx$ is used to translate the surface derivation of that premise into the core context $\nonterm{GC}$,
    which is then used in \textsc{CT-UnitTerm}.
